Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
PPLgrid

Statistically, the domain of convex polyhedra gives the better results, but
regularly yields greater invariants than the domains of octagons/intervals.
Experiences shows is it mostly due to the widening operator.
The Octagon domain appears to be much better than intervals.
\JH{Commenter les resultats}

Analysis of linear equalities (PKEQ) performs very fast compared
to other abstract domains, but yields very unprecise invariants.
The comparison between the domain of convex polyhedra and linear congruences
shows the percentage of points where the use of congruences refines the
invariant. This is the case for $1.04\%$ of the control points in $P_R$.

>>>>

Statistically, the domain of convex polyhedra gives the better results, but
commonly yields greater invariants than the domains of octagons/intervals;
this is a known weakness of its widening operator.
% DM Ici on pourrait citer Monniaux+Le Guen si c'etait publie!
The Octagon domain appears to be much better than intervals.
\JH{Commenter les resultats}

The analysis of linear equalities (PKEQ) performs very fast compared
to other abstract domains, but yields very imprecise invariants:
it only detects relations of the form $\sum a_i x_i = C$ where $a_i$ and $C$ are constants.
The comparison between the domain of convex polyhedra and linear congruences
shows the percentage of points where the use of congruences refines the
invariant. This is the case for $1.04\%$ of the control points in $P_R$.
\DM{Je croyais qu'on ne pouvait pas utiliser PPLGRID?}
